Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-14 beamer/envolve.tex
init beamer

% !TEX root = ../beamer.tex
\section{Manufacturing Ecosystem Envolving}
\subsection{Envolving Aim \& Main Factors}
\begin{frame}{Manufacturing Ecosystem Envolving}{Envolving Aim \& Main Factors}

\end{frame}

\subsection{Rating Schema}
\begin{frame}{Manufacturing Ecosystem Envolving}{Rating Schema}

\end{frame}

\subsection{Recommand System}
\begin{frame}{Manufacturing Ecosystem Envolving}{Recommand System}

\end{frame}

\subsection{User Introduction \& Elimination}
\begin{frame}{Manufacturing Ecosystem Envolving}{User Introduction \& Elimination}

\end{frame}

>>>>

% !TEX root = ../beamer.tex
\section{Manufacturing Ecosystem Envolving}
\subsection{Envolving Aim \& Main Factors}
\begin{frame}{Envolving Aim \& Main Factors}{Manufacturing Ecosystem Envolving}
\onslide<+->{The aim of envolving in the Ecosystem is to: \begin{itemize}
\item optimize the utilize of manufacturing resources
\item find the adaptive operating model for enterprises
\item filter out the underisable enterprises.
\end{itemize}}
\onslide<+->{
\begin{block}{Main Factors for Envolving}
\begin{itemize}
\item Rating Schema;
\item Recommand System and
\item Criterion of User Introduction and Elimination
\end{itemize}
\end{block}}
\end{frame}

\subsection{Rating Schema}
\begin{frame}{Rating Schema}{Manufacturing Ecosystem Envolving}
\onslide<+->{Rating user's rank is the base of Recommand System, so the rating schema should be designed. Most modern rating systems are derived from Elo's model:}
\onslide<+->{\begin{numcases}{}
E_A = \frac{1}{1+10^{\frac{R_B-R_A}{400}}} \\
R_A := R_A + K(S_A - E_A) \\
E_B = \frac{1}{1+10^{\frac{R_A-R_B}{400}}} \\
R_B := R_B + K(S_B - E_B)
\end{numcases}}
\end{frame}

\subsection{Recommand System}
\begin{frame}{Recommand System}{Manufacturing Ecosystem Envolving}
\onslide<+->{There are two scenarios in recommendation:
\begin{itemize}
\item Service Searching
\item Platform priority setting
\end{itemize}
}
\onslide<+->{
	Collaboration Filtering is popular method used in recommand system:
	\begin{equation}
	\begin{split}
	\min_{p_*,q_*,b_*} & \sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 \\
		& + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
	\end{split}
	\end{equation}
	\begin{numcases}{}
	\hat{r}_{ui} = b_{ui} + p^T_uq_i \\
	b_{ui} = \mu + b_u + b_i  \\
	\kappa =\{(u,i)|r_{ui} \text{is known}\} 
	\end{numcases}
}
\end{frame}

\subsection{User Introduction \& Elimination}
\begin{frame}{User Introduction \& Elimination}{Manufacturing Ecosystem Envolving}
\onslide<+->{
	Ecosystem envolving need a good user introduction and elimination method with:
}
\onslide<+->{
	\begin{block}{Envolving}
	\begin{itemize}
	\item Reinforcement Learning
	\item Control
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Envision of the Ecosystem}
\begin{frame}{Envision}{After a long running time and the system seems stable}
\onslide<+->{
	With poper scheduling and envolving, Cloud Manufacturing Ecosystem running with a stable mode:
	\begin{block}{Stable System Envision}
	\begin{itemize}
		\item Less-Popular manufacturing services are utilized instead of idleness with Coupon
		\item Products are manufactured with appropriate resource
		\item High rank users in different type of manufacturing resource lead the industrial chain
		\item Good operating models appear and being refined with time goes by
	\end{itemize}
	\end{block}
}
\end{frame}

### 2015-10-14 beamer/intro.tex
main struct
init beamer

\subsection{lalala}

\begin{frame}{First Slide Title}{Optional Subtitle}
  \begin{itemize}
  \item {
    My first point.
  }
  \item {
    My second point.
  }
  \end{itemize}
\end{frame}

\subsection{Second Subsection}

% You can reveal the parts of a slide one at a time
% with the \pause command:
\begin{frame}{Second Slide Title}
  \begin{itemize}
  \item {
    First item.
    \pause % The slide will pause after showing the first item
  }
  \item {   
    Second item.
  }
  % You can also specify when the content should appear
  % by using <n->:
  \item<3-> {
    Third item.
  }
  \item<4-> {
    Fourth item.
  }
  % or you can use the \uncover command to reveal general
  % content (not just \items):
  \item<5-> {
    Fifth item. \uncover<6->{Extra text in the fifth item.}
  }
  \end{itemize}
\end{frame}

>>>>

\subsection{Cloud Manufacturing}
\begin{frame}{Brief Introduction}{Cloud Manufacturing}
\onslide<+->{Cloud manufacturing combines technologies such as
\begin{itemize}
\item Internet of Things
\item Cloud computing
\item Semantic Web
\item Virtualisation
\item Service-oriented technologies
\end{itemize}
}

\onslide<+->{Aims the manufacturing process to be
\begin{itemize}
\item networked
\item intelligent
\item service-oriented
\item knowledge-based
\item energy efficient
\end{itemize}}
\end{frame}

\subsection{Current Items}

\begin{frame}{Current Items}{National High-Tech. R\&D Program, China}
\textbf{Item}: \textit{Key Technologies Research on Cloud Manufacturing Platform for Group Enterprises (No. 2015AA042101)}
\begin{block}{Main Tasks}
  \begin{itemize}
  \item Business model and standard making in group enterprises;
  \item Multi-tenancy technology for on-demand useage;
  \item Platform development for enterprises (Cooperate);
  \item Application demonstration (Cooperate).
  \end{itemize}
\end{block}
\end{frame}

\begin{frame}{Current Items}{National Natural Science Fundation, China}
\textbf{Item}: \textit{BOSS based Product Manufacturing-service Modeling and Cloud Platform Guided Service-network Evolving (No. 71571161)}
\begin{block}{Main Tasks}
\begin{itemize}
\item Methodology study for standard Manufacturing-service;
\item Methodology study for Manufacturing-service evalution;
\item Optimize the matching for service and task;
\item Explore the evolution of Manufacturing-service.
\end{itemize}
\end{block}
\end{frame}

### 2015-10-14 beamer/preliminary.tex
init beamer

\subsection{Another Subsection}

\begin{frame}{Blocks}
\begin{block}{Block Title}
You can also highlight sections of your presentation in a block, with it's own title
\end{block}
\begin{theorem}
There are separate environments for theorems, examples, definitions and proofs.
\end{theorem}
\begin{example}
Here is an example of an example block.
\end{example}
\end{frame}

>>>>

\subsection{Cloud Manufacturing}
\begin{frame}{Ecosystem Main Struct}{Cloud Manufacturing}
\only<1>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
	\caption{Princiapl Struct of Cloud Manufacturing Ecosystem}
	\end{figure}
}
\only<2>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=40 0 450 250,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\only<3>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=0 160 500 450,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\end{frame}

\begin{frame}{Standardization \& Decomposition}{Service \& Task}
\onslide<+->{
	Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub. 
}
\onslide<+->{
	\begin{block}{Related Methods}
	\begin{itemize}
	\item Resource Virtualization
	\item Construct Virtual Resource into Service Unit
	\item Service Standardization
	\item Order Decomposition into Tasks
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Roles}
\begin{frame}{Usual Names}{Roles}
\onslide<+->{\small
	\begin{description}
	\item[User] The main role in Cloud Manufacturing, usually acts as Seller or Buyer;
	\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service;
	\item[Buyer] The temporary role in a transaction, which submits the allocated part of manufacturing task;
	\item[Administrator] The role that gets the work for the operation and maintenance of the platform.
	\end{description}
}
\onslide<+->{
\begin{table}[htbp]
  \centering\scriptsize
    \begin{tabular}{lcc}
    \toprule
        &  Seller & Buyer  \\
    \midrule
    Generalized User & $\surd$ & $\surd$  \\
    Enterprise User & $\surd$ &  \\
    Customer User& & $\surd$ \\
    \bottomrule
    \end{tabular}%
\end{table}
}
\end{frame}

\subsection{Operating Model}
\begin{frame}{Overview}{Operating Model}
\only<1>{The style the Cloud Manufacturing Ecosystem appears mainly depends on the way the operating model takes, therefore, research on features and issues in the Ecosystem would be taken within the scope of operating model we are going to set up in:
\begin{block}{Operating Model Components}
\begin{itemize}
\item Order Flow
\item User Rank
\item Platform
\end{itemize}
\end{block}}
\only<2>{\begin{figure}
\tiny\centering\resizebox{\textwidth}{!}{
\input{figures/operatingmodel.tex}}
\caption{Overview of the Operating Model}
\end{figure}}
\end{frame}

\begin{frame}{Order Flow}{Operating Model}
\only<1>{Each order appears when Users make transaction in the platform, it might then go through different paths:
\begin{figure}
\tiny\centering
\resizebox{\textwidth}{!}{\input{figures/simple_order_flow.tex}}
\caption{Simple Flow Chart of Order}
\end{figure}
}
\end{frame}

\begin{frame}{User Rank}{Operating Model}
\onslide<+->{User Rank provides the basis to make the recommandation and to get more permission, the rank will increase or decrease by good or bad performance in each transaction}
\onslide<+->{
\begin{equation}
  \begin{cases}
      Rank_{[T+1]} = Rank_{[T]} + Gain - Lose, & T \geqslant 1\\
      Rank_{[0]} = Rank_{[init]}
  \end{cases}
\end{equation}
}
\end{frame}

\begin{frame}{Platform}{Operating Model}
\onslide<+->{
	Cloud Manufacturing Platform is mantained by Administrators with:
}
\onslide<+->{
	\begin{block}{Platform Maintenances}
	\begin{itemize}
	\item Decompose Orders into Tasks
	\item Construct Standard Services
	\item Introduce/Eliminate Users
	\item Distribute Permissions
	\item Adjust Resource Useage by Recommandations and Bonus
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Data Science Tools}
\begin{frame}{Data Science Tools}
\onslide<+->{In such Cloud Manufacturing Operating Model, there comes massive amount of data:\begin{itemize}
  \item Transaction histroy;
  \item Ranking histroy;
  \item Status of resources, services, orders and tasks;
  \item Decision pattern and so on.
\end{itemize}}
\onslide<+->{
	A bunch of Data Science Tools can be helpful:
	\begin{block}{Useful Data Science Tools}
	\begin{itemize}
	\item Data Analysis (collection, cleaning, modeling\&algorithms)
	\item Data Warehousing
	\item Machine Learning
	\item Social Network Anaysis
	\end{itemize}
	\end{block}
}
\end{frame}

%\begin{frame}{Blocks}
%\begin{block}{Block Title}
%You can also highlight sections of your presentation in a block, with it's own title
%\end{block}
%\begin{theorem}
%There are separate environments for theorems, examples, definitions and proofs.
%\end{theorem}
%\begin{example}
%Here is an example of an example block.
%\end{example}
%\end{frame}

### 2015-10-14 beamer/schedule.tex
init beamer

% !TEX root = ../beamer.tex
\section{Services Scheduling}
\subsection{Standardization}
\begin{frame}{Services Scheduling}{Main}

\end{frame}
\subsection{Decision Making Support}
\begin{frame}{Services Scheduling}{Decision Making Support}

\end{frame}

\subsection{Matching Regualtion}
\begin{frame}{Services Scheduling}{Matching Regualtion}

\end{frame}

\subsection{Platform Assistance}
\begin{frame}{Services Scheduling}{Platform Assistance}

\end{frame}

>>>>

% !TEX root = ../beamer.tex
\section{Services Scheduling}
\subsection{Standardization}
\begin{frame}{Support Module}{Service Standardization}
\onslide<+->{The basic support modules for Service Standardization include:
\begin{block}{Basic Modules}
\begin{itemize}
\item Resource Virtualization \& Encapsulation
\item Clustering Method
\item Refine Method
\end{itemize}
\end{block}}

\onslide<+->{
Important support Service Scheduling process modules:
\begin{block}{Support Moudles}
\begin{itemize}
\item Decision Making Support
\item Matching Regualtion
\item Platform Assistance
\end{itemize}
\end{block}
}
\end{frame}

\subsection{Decision Making Support}
\begin{frame}{Decision Making Support}{Services Scheduling}
\onslide<+->{
	Users in Cloud Manufacturing platfrom will make decision for:
}
\onslide<+->{
	\begin{itemize}
	\item Order acceptance;
	\item Task decomposition;
	\item Task (re-)outsourscing;
	\item Seller selection;
	\item Manufacturing arrangement.
	\end{itemize}
}
\end{frame}

\subsection{Matching Regualtion}
\begin{frame}{Matching Regualtion}{Services Scheduling}
\onslide<+->{
	In order to recommand poper manufacturing service with the order user submitted, Cloud Manufacturing platfrom should provide best-match solution, thus service search engine need to adopt a series of well designed matching regulations.
}
\end{frame}

\subsection{Platform Assistance}
\begin{frame}{Platform Assistance}{Services Scheduling}
\onslide<+->{
	Administrator assist platform to set priority for tasks and services, so the user will considerd:
}
\onslide<+->{
	\begin{itemize}
	\item How to make priority setting recommendation
	\item How to make decisions with the recommendation
	\end{itemize}
}
\end{frame}

### 2015-10-14 envolve.tex
init beamer

% !TEX root = Eco-Model.tex
\section{Manufacturing Ecosystem Envolving} % (fold)
\label{sec:envolve}
\subsection{Envolving Aim and Main Factors} % (fold)
\label{sub:envolving_aim}
The aim of envolving in the Ecosystem is to optimize the utilize of manufacturing resources, find the adaptive operation mode for enterprises and filter out the underisable enterprises. In the process of envolving related 
main factors including:
\begin{inparaenum}[1)]
\item Rating Schema;
\item Recommand System and
\item Criterion of User Introduction and Elimination
\end{inparaenum}

@@

\begin{numcases}{}
\min_{p_*,q_*,b_*}\sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
\label{equ:latent1}\\
\hat{r}_{ui} = b_{ui} + p^T_uq_i \label{equ:latent2}\\
b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
\kappa =\{(u,i)|r_{ui}\text{is known}\} \label{equ:latent4}
\end{numcases}
This model \eqref{equ:latent1} - \eqref{equ:latent4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet. \eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector. This model can be solved by Gradient Descent method and $p_*,q_*,b_*$ are the optimal value.

@@

\subsection{User Introduction and Elimination} % (fold)
\label{sub:control}
Finally, administrators make the strategy for introduction and elimination of users, they can easily set a baseline and assess the user to make the decision.  
% subsection control (end)
% section envolve (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Manufacturing Ecosystem Envolving} % (fold)
\label{sec:envolve}
\subsection{Envolving Aim and Main Factors} % (fold)
\label{sub:envolving_aim}
The aim of envolving in the Ecosystem is to optimize the utilize of manufacturing resources, find the adaptive operating model for enterprises and filter out the underisable enterprises. In the process of envolving related 
main factors including:
\begin{inparaenum}[1)]
\item Rating Schema;
\item Recommand System and
\item Criterion of User Introduction and Elimination
\end{inparaenum}

@@

\begin{numcases}{}
\min_{p_*,q_*,b_*}\sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
\label{equ:latent1}\\
\hat{r}_{ui} = b_{ui} + p^T_uq_i \label{equ:latent2}\\
b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
\kappa =\{(u,i)|r_{ui} \text{is known}\} \label{equ:latent4}
\end{numcases}
This model \eqref{equ:latent1} - \eqref{equ:latent4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet. \eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector. This model can be solved by Gradient Descent method and $p_*,q_*,b_*$ are the optimal value.

@@

\subsection{User Introduction and Elimination} % (fold)
\label{sub:control}
Finally, administrators make the strategy for introduction and elimination of users, they can easily set a baseline and assess the user to make the decision.  
% subsection control (end)

\subsection{Reinforcement Learning and Control} % (fold)
\label{sub:reinforcement_learning_and_control}
test figure

% subsection reinforcement_learning_and_control (end)
% section envolve (end)

### 2015-10-14 figures/simple_order_flow.tex
init beamer

% !TEX root = ../Eco-Model.tex
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going right,    % General flow is top-to-bottom
    node distance=6mm and 10mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, rectangle},
  proc/.style={base, text width=6em, minimum height=8em},
  term/.style={base, text width=5em, rounded corners, minimum height = 3ex},
  dproc/.style={proc, minimum height = 20ex},
  gathe/.style={draw, on chain, on grid, align=center, circle, minimum height=4ex, text width=0.5em, node distance=10mm and 8mm},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  sky/.style={coordinate, on chain, on grid, node distance=6mm and 60mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [term, fill = lcfree!25]              {Order};
\node [proc, join=by free]  (p1) {Task Hub};
\node [proc, dashed] (d) {};
\node [term, xshift = 12mm] (oc) {Order Check};
\node [term, join=by cong, fill = lccong!25]  {Submit};

\node [gathe, right=of d,yshift=5mm, xshift= 15mm] (g1) {};
\node [term, below=of d, yshift=15.5mm] (u1) {User 1};
\node [term, below=of u1] (u2) {User 2};
\node [below=-1mm of u2] (u3) {$\vdots$};
\node [term,below=of u3, yshift=-1mm] (u4) {User n};
\node [below=of u4,yshift=2.6mm] {User Cluster};
\node [gathe, below=of g1] (g2) {};
\node [coord, above=of g1, yshift=8mm] (c1) {};

@@

\draw [->, lcnorm] (u1.east) -- (g1.west);
\draw [->, lccong] (u1.east) -- (g2.west);
\draw [->, lcnorm] (u2.east) -- (g1.west);
\draw [->, lccong] (u2.east) -- (g2.west);
\draw [->, lcnorm] (u4.east) -- (g1.west);
\draw [->, lccong] (u4.east) -- (g2.west);
\draw [->, lcnorm] (g1) -- (c1) -- node [black, near end, yshift=0.75em, it]
    {(Outsourcing)} ++(-3.5cm,0) -| (p1) ;

>>>>

% !TEX root = ../Eco-Model.tex
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going right,    % General flow is top-to-bottom
    node distance=1.6em and 2.5em, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, rectangle},
  proc/.style={base, text width=6em, minimum height=8em},
  term/.style={base, text width=5em, rounded corners, minimum height = 3ex},
  dproc/.style={proc, minimum height = 20ex},
  gathe/.style={draw, on chain, on grid, align=center, circle, minimum height=4ex, text width=0.5em, node distance=10mm and 8mm},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  sky/.style={coordinate, on chain, on grid, node distance=6mm and 60mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [term, fill = lcfree!25]              {Order};
\node [proc, join=by free]  (p1) {Task Hub};
\node [proc, dashed] (d) {};
\node [term, xshift = 12mm] (oc) {Order Check};
\node [term, join=by cong, fill = lccong!25]  {Submit};

\node [gathe, right=of d,yshift=5mm, xshift= 4em] (g1) {};
\node [term, below=of d, yshift=4.1em] (u1) {User 1};
\node [term, below=of u1] (u2) {User 2};
\node [below=-1mm of u2] (u3) {$\vdots$};
\node [term,below=of u3, yshift=-1mm] (u4) {User n};
\node [below=of u4,yshift=2.6mm] {User Cluster};
\node [gathe, below=of g1] (g2) {};
\node [coord, above=of g1, yshift=2em] (c1) {};

@@

\draw [->, lcnorm] (u1.east) -- (g1.west);
\draw [->, lccong] (u1.east) -- (g2.west);
\draw [->, lcnorm] (u2.east) -- (g1.west);
\draw [->, lccong] (u2.east) -- (g2.west);
\draw [->, lcnorm] (u4.east) -- (g1.west);
\draw [->, lccong] (u4.east) -- (g2.west);
\draw [->, lcnorm] (g1) -- (c1) -- node [black, near end, yshift=0.75em, it]
    {(Outsourcing)} ++(-9em,0) -| (p1) ;

### 2015-10-14 schedule.tex
init beamer

\subsection{Matching Regulation} % (fold)
\label{sub:matching_regulation}
There are two main parts, recommendation for resource matching and resource prediction, of resources recommendation module that we will discuss in \autoref{sub:recommand_system}, and the first one depicted the situation where user in buyer role will always encounter.

>>>>

\subsection{Matching Regulation} % (fold)
\label{sub:matching_regulation}
There are two main parts, recommendation for resource matching and idle resource, of resources recommendation module that we will discuss in \autoref{sub:recommand_system}, and the first one depicted the situation where user in buyer role will always encounter.
